Future challenges for Research Software Engineering

### 2025-04-14 future_challenges_for_RSEng.tex
add a note about outsourcing

\subsubsection{Which challenges will still persist}
The workshop participants expect that there will still be budgeting and administrative hurdles to creating
permanent and well-funded RSE teams.
While we hope that the barrier to researchers diminishes, the workshop participants
still expect some work to do. We hope that the compartmentalization that occurs will help researchers reprioritize their workload.
An upcoming challenge will be that, with the emergence of more dedicated RSE units,
networking between them will come into the foreground, because there should be a strong need to share best practices
among institutions with succesful RSE Teams.
On a more organisational level, we expect the sharing of models, to fit the different organizational constraints.

@@

>>>>

\subsubsection{Which challenges will still persist}
The workshop participants expect that there will still be budgeting and administrative hurdles to creating
permanent and well-funded RSE teams.
While we hope that the barrier to researchers diminishes, the workshop participants
still expect some work to do. We hope that the compartmentalization that occurs will help researchers reprioritize their workload.
An upcoming challenge will be that, with the emergence of more dedicated RSE units,
networking between them will come into the foreground, because there should be a strong need to share best practices
among institutions with succesful RSE Teams.
On a more organisational level, we expect the sharing of models, to fit the different organisational constraints.

@@

FG-TEXT-START:
As outlined in [cite RSE group paper] not all universities need to opt for strengthening
the academic midlevel. Some might have chosen to set up external companies to outsource typical RSE tasks,
thereby providing career paths outside of academia.
FG-TEXT-END:
